Learning and Reputation under Monopoly and Duopoly: \\A Competing Bandits Approach

### 2018-08-16 paper/competing_bandits.tex
more cosmetic changes
whoops

Many modern online platforms simultaneously compete for users as well as learn from the users they manage to attract. For instance, Google Search and Bing compete for users in the search engine market yet at the same need to experiment with their search algorithms to learn what algorithms work the best. This creates a tradeoff between \textit{exploration} and \textit{competition} since firms need to experiment with potentially sub-optimal options for the benefit of gaining information to make better decisions tomorrow while at the same time firms need to incentivize consumers to select them over their competitors today.

@@

\noindent \textbf{firms} We suppose that the firms simply care about maximizing their expected market share (i.e. maximizing the number of $T$ agents who select them). We model the ``competition game" between firms as a simultaneous move game where both firms commit to a learning algorithm.

>>>>

Many modern online platforms simultaneously compete for users as well as learn from the users they manage to attract. For instance, Google Search and Bing compete for users in the search engine market yet at the same time need to experiment with their search algorithms to learn what algorithms work the best. This creates a tradeoff between \textit{exploration} and \textit{competition} since firms need to experiment with potentially sub-optimal options for the benefit of gaining information to make better decisions tomorrow while at the same time firms need to incentivize consumers to select them over their competitors today.

@@

\noindent \textbf{Firms} We suppose that the firms simply care about maximizing their expected market share (i.e. maximizing the number of $T$ agents who select them). We model the ``competition game" between firms as a simultaneous move game where both firms commit to a learning algorithm.
